\bf Probabilistic Forecasts in Hierarchical~Time~Series

### 2020-01-28 R1/Response.tex

		The observation regarding the constraints not holding on the log scale is correct.  When series are transformed to the log scale, forecasts are first produced on the log scale and these are back transformed to the original scale (possibly with bias correction) prior to carrying out reconciliation.  Therefore while all modelling is done on the log scale, all reconciliation is carried out on the original scale.  The fact that the constraints do not hold on the log scale is therefore not relevant.\\

		On re-reading the paper we do agree with the referee that there is scope for confusion here.  Therefore we have added some additional exposition to the beginning of section 4.1.  The aim here is to make it clear that after producing forecasting on some tranformed scale, the correct sequence of steps is to 1) back-transform to the original scale, 2) bias correct and 3) reconcile. \\

		\textit{When the empirical evaluation is focused on bias, then it would make sense to include an error that measures bias in addition to the squared error.}\\

		We now also report the total error for all methods to highlight bias.  Here we see that bias correction method 1 removes bias, while bias correction method 2 in fact worsens bias.  A new insight that we are able to make is to recognise that reconciliation without bias correction can still mitigate bias.  For example, even if bias correction is not used at all, OLS reconciliation significantly reduces bias for both the log transformation and Box Cox transformation.  This is likely to occur since bias lies in a direction that is almost orthogonal to the coherent subspace.\\

@@

	    \textit{The best performing reconciliation method is MinT with shrinkage, but the authors never state	the value of the shrinkage parameter or how it was chosen.  Similarly, they compare with variance scaling without explaining what they mean by variance scaling.}\\

	    The shrinkage estimator is that of Sch\"afer and Strimmer~(2005). Details on this method (including the choice of shrinkage parameter) are now provided.  Similarly, we now provide more detail on variance scaling, which simply refers to using the variance of one step ahead in-sample forecast errors.\\

	    \textit{In addition to the above mentioned shortcomings, I think the authors should reconsider their empirical evaluation. Maybe a second case study or a simulation study is needed to show the value of the geometric insights provided. We already know that MinT is better than OLS and WLS. What is the new and better reconciliation approach that has come from the geometric insights?}\\

		The objective of this paper is not to propose a new and better reconciliation approach.  Rather it is to establish new results that lead to clearer understanding of the properties of existing methods that in turn motivate research into new methods.  Therefore, while the paper does not include a new method, it does provide insights into how new methods should (or should not) be developed.  For examples of this, see the discussion on page 19 just before Section 4.1 and comments in the conclusion.\\

		In this paper, the purpose of the empirical evaluation is to provide a demonstration of the theoretical results that we have established.  We agree that this could be improved.  We have greatly expanded Section 5.2 to more clearly investigate three different loss functions and demonstrate the different ways in which reconciliation methods can be considered optimal.\\

@@

		Improving the existing empirical application in the ways suggested by the referee has lengthened the paper considerably.  Therefore, we prefer to refrain from including a second empirical demonstration.\\

		\item \textit{Improvement guarantees: The boxplot in Figure 8 shows that OLS always improves MSE, while this is not the case for the other reconciliation approaches. To gain a better understanding of the implications of Theorem 3.2, it would be useful to show that the other approaches always
		improve accuracy in their transformed spaces.}\\

	    We now expand section 5.2 to report results for three different error metrics.  Furthermore we have added additional insights in Section 3.4 that are now also demonstrated in this section.  In particular we show that while the distance reducing property of Theorem 3.2 depends entirely on the choice of loss function, minimising the expected loss function can always be achieved by a MinT approach and does not depend on the weights used in a loss function.\\

@@

		\textit{What is the interpretation of the transformed spaces and can the authors make the connection	between these spaces and the choice of reconciliation approach and error measure more clear?}\\

	    Reflecting on this issue has led us towards making a number of changes.  To reiterate, we may define a loss function based on the notion of Euclidean distance.  In this case an orthogonal projection is guaranteed to lead to reconciled forecasts that are better than base forecasts.  Alternatively we may define a more general loss function, for instance by taking weights into account.  We now consider two such loss functions, one based on the structure of the hierarchy (so-called `structural scaling') and another based on average spend in each region.  The latter of these can be interpreted in terms of tourism revenue rather than tourism numbers.  In this case, it is an orthogonal projection in the \textit{transformed} space that is guaranteed to improve upon base forecasts with respect to this loss function.\\

	    We also consider the property of minimising expected loss when the loss is function based on Euclidean distance.  This can be achieved by the MinT estimator.  We now provide a new result proving that minimising the expected loss in a transformed space in fact leads to the same MinT estimator.\\

### 2020-01-28 R1/Letter.tex
minor changes to response and letter to reflect third loss function

Please find attached a revised manuscript for ``Forecast reconciliation: a geometric view with new insights on bias correction" by Anastasios Panagiotelis, Puwasala Gamakumara, George Athanasopoulos and Rob Hyndman for your consideration for publication in International Journal of Forecasting. We are very excited to have been given the opportunity to revise and resubmit. We carefully considered the comments offered by the two reviewers. Herein, we briefly summarize the major changes in the revision:
\begin{enumerate}
	\item We have greatly expanded the empirical study including more measures of forecast accuracy (including those specifically measuring bias).  This has led to the insight that reconciliation alone can in fact reduce the bias of an estimator.  We also now also report where differences in forecast accuracy are statistically significant.
	\item We introduce some new results about MinT that explicitly makes the connection between trace minimisation and minimises a loss function based on Euclidean distance.  We also prove a new result that MinT minimises expected loss for loss functions based on generalised Euclidean distance.  This result is demonstrated in an expanded empirical application in section 5.2 that includes a wider range of loss functions. 
	\item We now reflect on some issues that were not discussed in the previous version of the manuscript including the role of non-negative forecasts, and state-space models. 
\end{enumerate}

>>>>

Please find attached a revised manuscript for ``Forecast reconciliation: a geometric view with new insights on bias correction" by Anastasios Panagiotelis, Puwasala Gamakumara, George Athanasopoulos and Rob Hyndman for your consideration for publication in International Journal of Forecasting. We are very excited to have been given the opportunity to revise and resubmit. We carefully considered the comments offered by the two reviewers. Herein, we briefly summarize the major changes in the revision:
\begin{enumerate}
	\item We have greatly expanded the empirical study including more measures of forecast accuracy (including those specifically measuring bias).  This has led to the insight that reconciliation alone can in fact reduce the bias of an estimator.  We also now also report where differences in forecast accuracy are statistically significant.
	\item We introduce some new results about MinT that explicitly make the connection between trace minimisation and minimising a loss function based on Euclidean distance.  We also prove a new result that MinT minimises expected loss for loss functions based on generalised Euclidean distance.  This result is demonstrated in an expanded empirical application in section 5.2 that includes a wider range of loss functions. 
	\item We now reflect on some issues that were not discussed in the previous version of the manuscript including the role of non-negative forecasts, and state-space models. 
\end{enumerate}
